Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2013-03-23 documents/mixtures/mixture_models.tex
add footnote to scipy
dstn style -> hogg style

\cite{ciotti} give an equation for $\alpha^{\ser(n)}$ in their
equation 5:
\begin{eqnarray}
\gamma(2 n, \alpha^{\ser(n)}) &=& \frac{\Gamma(2 n)}{2}
\end{eqnarray}
where $\gamma$ is the \emph{left} or \emph{lower} incomplete gamma function,
\begin{eqnarray}
\gamma(a, x) &=& \int_0^x \exp(-t) \, t^{a-1} \, \mathrm{d} t \quad .
\end{eqnarray}
Fortunately for us, this can be evaluated using
\begin{eqnarray}
\alpha^{\ser(n)} &=& \texttt{gammaincinv}(2 n, \, \frac{1}{2})
\end{eqnarray}
using the \texttt{gammaincinv} (inverse incomplete gamma) function in the
\project{scipy.special} library.

>>>>

The general equation for $\alpha^{\ser(n)}$ is (\citealt{ciotti} equation~5):
\begin{eqnarray}
\gamma(2 n, \alpha^{\ser(n)}) &=& \frac{\Gamma(2 n)}{2}
\\
\gamma(q, x) &\equiv& \int_0^x \exp(-t) \, t^{q-1} \, \mathrm{d}t
\quad ,
\end{eqnarray}
where $\gamma(\cdot)$ is the \emph{left} or \emph{lower} incomplete
gamma function.  Fortunately for us, this can be evaluated using
\begin{eqnarray}
\alpha^{\ser(n)} &=& \texttt{gammaincinv}(2 n, \, \frac{1}{2})
\end{eqnarray}
using the \texttt{gammaincinv} (inverse incomplete gamma) function in the
\project{scipy.special} library.
